Data Exploration

### 2018-11-27 src/data_exploration.Rmd
density plot with background and presence env. data

>>>>

## density plot with background and presence env. data

Inspired by Merrow 2013 - top paragraph of page 1063 (are the species observations uniformly distributed over the background, or are they skewed)

```{r}
ggplot(pres_env, aes(x = temp_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/temp_depth_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = temp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/temp_surface_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = chl_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/chl_surface_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = chl_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/chl_depth_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = salinity_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/salinity_surface_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = salinity_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/salinity_depth_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = o2_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/o2_surface_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = o2_depth)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/o2_depth_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = mlp_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/mlp_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

```{r}
ggplot(pres_env, aes(x = ssh_surface)) + geom_density(na.rm = TRUE, colour = "red") + geom_density(data=background_env, na.rm = TRUE, colour = "blue")
dev.copy(png,"../output/env/simple_plots/ssh_backvspres.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```
